Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-11-14 awipev-CO2.Rmd
server text updated

- Serveur : awipev-co2 (193.50.85.104)
- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer).
- Pour se connecter à awipev-co2.obs-vlfr.fr
    - ssh awipev@awipev-co2.obs-vlfr.fr
- Intervention sur le serveur :
    - ssh awipev@awipev-co2.obs-vlfr.fr
    - rebooting Ubuntu server: sudo shutdown -r now
    - to check versions:
        - dpkg -l | grep shiny
        - dpkg -l | grep r-base
    - To update Ubuntu, R and its packages:
        - sudo su
        - apt-get upgrade
    - To restart shiny server: sudo systemctl restart shiny-server
    - update shiny server: follow procedure detailed on the shiny web page

@@

- Every night at 01:00 (?) two data files ("all sensors" and AT) are sent by ftp to:
    - awipev-co2.obs-vlfr.fr
    - User name: nydata
    - password:
- Every hour a crontab action runs the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files added each day around 01:00 and cleans the data
- Every night at 03:00 the web page is generated
- Every night at 05:00 the files are copied to gattuso’s iMac

@@

si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “- -delete” à la commande rsync # m h dom mon dow command 
00 */1 * * * cd ; R - -vanilla < ny-alesund/R/ny-alesund_cc.R

00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/awipev-co2_web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

>>>>

- Serveur : awipev-co2 (193.50.85.104)
- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer).
- Pour se connecter à awipev-co2.obs-vlfr.fr
        - ssh awipev@awipev-co2.obs-vlfr.fr
- Intervention sur le serveur :
        - ssh awipev@awipev-co2.obs-vlfr.fr
        - rebooting Ubuntu server: sudo shutdown -r now
        - to check versions:
            - dpkg -l | grep shiny
            - dpkg -l | grep r-base
        - To update Ubuntu, R and its packages:
            - sudo su
            - apt-get upgrade
        - To restart shiny server: sudo systemctl restart shiny-server
        - update shiny server: follow procedure detailed on the shiny web page Data processing

@@

- Every night at 01:00 (?) two data files ("all sensors" and AT) are sent by ftp to:
      - awipev-co2.obs-vlfr.fr
      - User name: nydata
      - password:

@@

si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command

- (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
00 01 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R

- (At 03:00, web page is generated)
00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1

- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud/Exp168)
00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

- (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
